The Splashback Radius of Planck-SZ clusters

### 2019-03-13 Paper_v2/RSP_paper_new.tex
soften the abstract further

\begin{abstract}
We present evidence for the existence of the splashback radius in galaxy
clusters selected using the Sunyaev-Zeldovich effect, {\bf a sample unaffected by
systematics related to cluster finding in the optical wavelength range.} We show
that the deprojected cross-correlation of galaxy clusters found in the Planck
survey with galaxies detected photometrically in the Pan-STARRS survey, shows a
sharp steepening feature (a logarithmic slope steeper than $-3$), which we
associate with the splashback radius. We infer the three-dimensional splashback
radius for the SZ cluster sample to be $r_{\rm sp}=1.85_{-0.30}^{+0.26}$
$\mpch$, where the cluster sample has an average halo mass $M_{\rm
500c}=3.0\times10^{14}\msunh$ at an average redshift of $z=0.18$.  The inferred
value of the splashback radius appears consistent with the expected location
for dark matter halos in the standard cold dark matter paradigm. However, given
the limited precision of our measurements, we cannot conclusively confirm or
rule out the smaller splashback radius measured so far in the literature for
optically selected galaxy clusters. We show that the splashback radius does not
depend upon the galaxy magnitude for galaxies fainter than $M_i-5\log
h=-19.44$, and is present at a consistent location in galaxy populations
divided by color. The presence of the splashback radius in the star-forming
galaxy population could potentially be used to put lower limits on the
quenching timescales for galaxies. We can marginally rule out the contamination
of the star-forming galaxy sample by quenched galaxies, but the results would
need further verification with deeper datasets.

>>>>

\begin{abstract}
We present evidence for the existence of the splashback radius in galaxy
clusters selected using the Sunyaev-Zeldovich effect, {\bf a sample unaffected by
systematics related to cluster finding in the optical wavelength range.} We show
that the deprojected cross-correlation of galaxy clusters found in the Planck
survey with galaxies detected photometrically in the Pan-STARRS survey, shows a
sharp steepening feature (a logarithmic slope steeper than $-3$), which we
associate with the splashback radius. We infer the three-dimensional splashback
radius for the SZ cluster sample to be $r_{\rm sp}=1.85_{-0.30}^{+0.26}$
$\mpch$, where the cluster sample has an average halo mass $M_{\rm
500c}=3.0\times10^{14}\msunh$ at an average redshift of $z=0.18$.  The inferred
value of the splashback radius appears marginally consistent with the expected location
for dark matter halos in the standard cold dark matter paradigm. However, given
the limited precision of our measurements, we cannot conclusively confirm or
rule out the smaller splashback radius measured so far in the literature for
optically selected galaxy clusters. We show that the splashback radius does not
depend upon the galaxy magnitude for galaxies fainter than $M_i-5\log
h=-19.44$, and is present at a consistent location in galaxy populations
divided by color. The presence of the splashback radius in the star-forming
galaxy population could potentially be used to put lower limits on the
quenching timescales for galaxies. We can marginally rule out the contamination
of the star-forming galaxy sample by quenched galaxies, but the results would
need further verification with deeper datasets.
